### 2025-12-09 review/response_250823.tex

		% 	\begin{subsubsection}{Alternating Optimization}
		% 		\label{sc:wsr_ao}
		% 		This approach updates $\mathbf{\Theta}$ and $\{\mathbf{W}_k\}_{k \in [K]}$ iteratively until convergence.
		% 		For a given precoder set, the passive beamforming subproblem is
		% 		\begin{maxi!}
		% 		{\scriptstyle{\mathbf{\Theta}}}{\sum_{k=1}^K \rho_k R_k}{\label{op:wsr_ris}}{\label{ob:wsr_ris}}
		% 		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
		% 	\end{maxi!}
		% 		which can be solved optimally by Algorithm \ref{ag:rcg} with the partial derivative given in Lemma \ref{lm:wsr}.

		% 		\begin{lemma}
		% 			\label{lm:wsr}
		% 			The partial derivative of \eqref{ob:wsr_ris} with respect to \gls{bd}-\gls{ris} block $g$ is
		% 			\begin{equation}
		% 				\label{eq:gradient_eucl_wsr}
		% 				\frac{\partial \rho_k R_k}{\partial \mathbf{\Theta}_g^*} = \sum_{k=1}^K \rho_k {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{Q}_k^{-1} {\mathbf{H}^{(kk)}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \bigl({\mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}}} - {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{-1} \sum_{j \ne k} {\mathbf{H}^{(kj)}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}}\bigr),
		% 			\end{equation}
		% 			where $\mathbf{E}_k = \bigl(\mathbf{I} + {\mathbf{W}_k^\mathsf{H}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k {\mathbf{H}^{(kk)}} \mathbf{W}_k\bigr)^{-1}$ is the error matrix of receiver $k$.
		% 		\end{lemma}

		% 		\begin{proof}
		% 			\label{pf:wsr}
		% 			The differential of $f = \sum_{k=1}^K \rho_k R_k$ with respect to $\mathbf{\Theta}_g^*$ is
		% 			\begin{align*}
		% 				\partial f
		% 				 & = \sum_{k=1}^K \rho_k \tr \Bigl\{ \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \Bigl( \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)}  + \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(k)} - \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)}                                                            \\
		% 				 & \quad \times \sum_{j \ne k} \Bigl(\mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} + \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \Bigr) \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \Bigr) \mathbf{W}_k \Bigr\}                                                \\
		% 				 & = \sum_{k=1}^K \rho_k \Bigl( \tr \Bigl\{ \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H}\Bigr\} + \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(k)\mathsf{H}} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \partial \mathbf{\Theta}_g \Bigr\} \\
		% 				 & \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kj)} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \partial \mathbf{\Theta}_g^\mathsf{H} \Bigr\}                                                                                                                                      \\
		% 				 & \quad - \tr \Bigl\{ \sum_{j \ne k} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{W}_j \mathbf{W}_j^\mathsf{H} \mathbf{H}^{(kj)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}^{(kk)} \mathbf{W}_k \mathbf{E}_k \mathbf{W}_k^\mathsf{H} \mathbf{H}^{(kk)\mathsf{H}} \mathbf{Q}_k^{(-1)} \mathbf{H}_{\mathrm{B},g}^{(k)} \partial \mathbf{\Theta}_g \Bigr\} \Bigr),
		% 			\end{align*}
		% 			and the corresponding complex derivative is \eqref{eq:gradient_eucl_wsr}.
		% 		\end{proof}

		% 		For a given $\mathbf{\Theta}$, problem \eqref{op:wsr} reduces to conventional precoding design for interference channel.
		% 		A closed-form iterative solution based on mutual information-\gls{mmse} relationship has been proposed in \cite{Shin2012,Negro2010} and we summarize the steps as follows.
		% 		At iteration $r$, the \gls{mmse} combiner at receiver $k$ is
		% 		\begin{equation}
		% 			\mathbf{G}_k^{(r)} = {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \bigl(\mathbf{Q}_k^{(r-1)} + {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)} {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}}\bigr)^{-1},
		% 		\end{equation}
		% 		the corresponding error matrix is
		% 		\begin{equation}
		% 			\mathbf{E}_k^{(r)} = \bigl(\mathbf{I} + {\mathbf{W}_k^{(r-1)\mathsf{H}}} {\mathbf{H}^{(kk)\mathsf{H}}} \mathbf{Q}_k^{(r-1)} {\mathbf{H}^{(kk)}} \mathbf{W}_k^{(r-1)}\bigr)^{-1},
		% 		\end{equation}
		% 		and the optimal precoder at transmitter $k$ is given by
		% 		\begin{equation}
		% 			\label{eq:precoder_wsr}
		% 			\mathbf{W}_k^{(r)} = \Bigl(\sum_{j=1}^K {\mathbf{H}^{(jk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)} \mathbf{G}_j^{(r)} \mathbf{H}^{(jk)} + \lambda_k^{(r)} \mathbf{I} \Bigr)^{-1} \times {\mathbf{H}^{(kk)\mathsf{H}}} {\mathbf{G}_j^{(r)\mathsf{H}}} \mathbf{\Omega}_k^{(r)},
		% 		\end{equation}
		% 		where $\mathbf{\Omega}_k^{(r)} = \rho_k {\mathbf{E}_k^{(r)-1}}$ is the mean-square error weight and $\lambda_k^{(r)}$ is the Lagrange multiplier retrievable by bisection \cite{Shin2012} or in closed form \cite{Negro2010}
		% 		\begin{equation}
		% 			\lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_{j=1}^K (\mathbf{Z}_{kj}^{(r)} - \mathbf{Z}_{jk}^{(r)}) \bigr)}{P_k},
		% 			% \lambda_k^{(r)} = \frac{\mathrm{tr}\bigl(\eta \mathbf{\Omega}_k^{(r)} \mathbf{G}_k^{(r)}{\mathbf{G}_k^{(r)\mathsf{H}}} + \sum_j \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}} - \mathbf{\Omega}_j^{(r)}\mathbf{T}_{jk}^{(r)} {\mathbf{T}_{jk}^{(r)\mathsf{H}}} \bigr)}{P_k},
		% 		\end{equation}
		% 		where $\mathbf{Z}_{kj}^{(r)} = \mathbf{\Omega}_k^{(r)}\mathbf{T}_{kj}^{(r)} {\mathbf{T}_{kj}^{(r)\mathsf{H}}}$ and $\mathbf{T}_{kj}^{(r)} = \mathbf{G}_k^{(r)} {\mathbf{H}^{(kj)}} \mathbf{W}_j^{(r)}$.

		% 		The computational complexity of solving subproblem \eqref{op:wsr_ris} by geodesic \gls{rcg} is $\mathcal{O}\bigl(I_\text{RCG} G (N_\mathrm{T} d^2 + N_\mathrm{T}^2 d + N_\mathrm{T}^2 N_\mathrm{R} + N_\mathrm{T} N_\mathrm{R}^2 + K (N_\mathrm{T} N_\mathrm{R} d + N_\mathrm{T} N_\mathrm{R} L) + I_\text{BLS}L^3)\bigr)$.
		% 		That is, $\mathcal{O}\bigl(N_\mathrm{S}\bigr)$ for \gls{d}-\gls{ris} and $\mathcal{O}\bigl(N_\mathrm{S}^3\bigr)$ for fully-connected \gls{bd}-\gls{ris}.
		% 	\end{subsubsection}

		% 	\begin{subsubsection}{Low-Complexity Solution}
		% 		\label{sc:wsr_lc}
		% 		Similar to Section \ref{sc:rate_lc}, we suboptimally decouple the beamforming design by first shape the channel by \gls{ris} for minimum leakage interference and then optimize the active beamforming.
		% 		The leakage interference minimization problem is formulated as
		% 		\begin{mini!}
		% 		{\scriptstyle{\mathbf{\Theta}}}{I = \sum_{k=1}^K \sum_{j \ne k} \left\lVert {\mathbf{H}}^{(kj)}_\mathrm{D} + {\mathbf{H}}^{(k)}_\mathrm{B} \mathbf{\Theta} {\mathbf{H}}^{(j)}_\mathrm{F} \right\rVert _{\mathrm{F}}^2}{\label{op:interference}}{\label{ob:interference}}
		% 		\addConstraint{\mathbf{\Theta}_g^\mathsf{H} \mathbf{\Theta}_g=\mathbf{I}, \quad \forall g,}{}{}
		% 	\end{mini!}
		% 		which can be solved iteratively in closed form.

		% 		\begin{proposition}
		% 			\label{pp:interference}
		% 			Starting from any feasible $\mathbf{\Theta}^{(0)}$, the sequence
		% 			\begin{equation}
		% 				\label{eq:ris_interference}
		% 				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
		% 			\end{equation}
		% 			monotonically decreases the objective function \eqref{ob:interference},
		% 			% converges to a stationary point of \eqref{op:interference},
		% 			where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are any left and right singular matrices of
		% 			\begin{equation}
		% 				\label{eq:auxiliary_interference}
		% 				\mathbf{M}_g^{(r)} = \sum_{k=1}^K \sum_{j \ne k} \bigl(\mathbf{B}_g^{(k)} \mathbf{\Theta}_g^{(r)} \mathbf{H}^{(j)}_{\mathrm{F},g} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} {\mathbf{D}^{(kj)(r)}_{g}}\bigr) {\mathbf{H}^{(j)\mathsf{H}}_{\mathrm{F},g}},
		% 			\end{equation}
		% 			where ${\mathbf{D}^{(kj)(r)}_{g}} = \mathbf{H}^{(kj)}_\mathrm{D} + \sum_{g'<g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r+1)} \mathbf{H}_{\mathrm{F},g'}^{(k)} + \sum_{g'>g} {\mathbf{H}_{\mathrm{B},g'}^{(k)\mathsf{H}}} \mathbf{\Theta}_{g'}^{(r)} \mathbf{H}_{\mathrm{F},g'}^{(k)}$ and  $\mathbf{B}_g^{(k)} = \lambda_1\bigl({\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}\bigr) \mathbf{I} - {\mathbf{H}^{(k)\mathsf{H}}_{\mathrm{B},g}} \mathbf{H}^{(k)}_{\mathrm{B},g}$.
		% 			Besides, when \eqref{eq:auxiliary_interference} converges, \eqref{eq:ris_interference} leads to a convergence of the objective function \eqref{ob:interference} towards a stationary point.
		% 		\end{proposition}
		% 		\begin{proof}
		% 			\label{pf:interference}
		% 			Minimizing \eqref{ob:interference} is equivalent to maximizing
		% 			\begin{align*}
		% 				f(\mathbf{\Theta}) & = - I + \sum_g \beta_g^{(k)} \tr \Bigl\{ \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \Bigr\}                                                                                                                                                                                                                                                                                                                                                                                          \\
		% 				                   & = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\}  - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\}                                                                                                                                                  \\
		% 				                   & \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\} \\
		% 				                   & \quad + \tr \Bigl\{ \sum_g \beta_g^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\}                                                                                                                                                                                                                                                                                                                                       \\

### 2025-12-09 review/response_250823.tex

		% 				                   & = \sum_{k=1}^K \sum_{j \ne k} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{H}_{\mathrm{D}}^{(kj)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)} \mathbf{\Theta}_g\Bigr\} - \tr \Bigl\{ \sum_g \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{D}}^{(kj)} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{\Theta}_g^\mathsf{H} \Bigr\}                                                                                                                                                   \\
		% 				                   & \quad - \tr \Bigl\{ \sum_{g_1=1}^G \sum_{g_2 \ne g_1} \mathbf{H}_{\mathrm{B},g_2}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g_1}^{(k)} \mathbf{\Theta}_{g_1} \mathbf{H}_{\mathrm{F},g_1}^{(j)} \mathbf{H}_{\mathrm{F},g_2}^{(j)\mathsf{H}} \mathbf{\Theta}_{g_2}^\mathsf{H}\Bigr\} + \tr \Bigl\{ \sum_g \mathbf{B}_{g}^{(k)} \mathbf{\Theta}_{g} \mathbf{H}_{\mathrm{F},g}^{(j)\mathsf{H}} \mathbf{H}_{\mathrm{F},g}^{(j)} \mathbf{\Theta}_{g}^\mathsf{H} \Bigr\},
		% 			\end{align*}
		% 			where $\mathbf{B}_{g}^{(k)} = \beta_g^{(k)} \mathbf{I} - \mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)}$ and the relaxation constant $\beta_g^{(k)}$ can be chosen arbitrarily.
		% 			One can choose $\beta_g^{(k)} = \lambda_1(\mathbf{H}_{\mathrm{B},g}^{(k)\mathsf{H}} \mathbf{H}_{\mathrm{B},g}^{(k)})$ to ensure the positive semi-definiteness of $\mathbf{B}_{g}^{(k)}$ and formulate a quadratic function to be maximized.
		% 			The remaining proof is similar to Appendix \ref{ap:power} and omitted here.
		% 		\end{proof}
		% 		Once the channel is shaped by \eqref{eq:ris_interference}, the active beamforming is retrieved iteratively by \eqref{eq:precoder_wsr}.
		% 		This two-stage solution avoids outer iterations and efficiently handles inner iterations.
		% 	\end{subsubsection}

		% 	\begin{subsubsection}{Simulation}
		% 		\begin{figure}[H]
		% 			\centering
		% 			\subfloat[Interference: $(4 \times N_\mathrm{S} \times 4)^5$]{
		% 				\label{fg:ic_interference_sx}
		% 				\resizebox{!}{5cm}{
		% 					\input{../assets/simulation/ic_interference_sx.tex}
		% 				}
		% 			}
		% 			\subfloat[WSR: $(2 \times 128 \times 2)^2, N_\mathrm{E} = 2$]{
		% 				\label{fg:ic_wsr_beamforming}
		% 				\resizebox{!}{5cm}{
		% 					\input{../assets/simulation/ic_wsr_beamforming.tex}
		% 				}
		% 			}
		% 			\\
		% 			\subfloat[WSR: $(4 \times N_\mathrm{S} \times 4)^5, N_\mathrm{E} = 4$]{
		% 				\label{fg:ic_wsr_sx}
		% 				\resizebox{!}{5cm}{
		% 					\input{../assets/simulation/ic_wsr_sx.tex}
		% 				}
		% 			}
		% 			\subfloat[WSR: $(N_\mathrm{T} \times 128 \times N_\mathrm{R})^{10}, N_\mathrm{E} = 2$]{
		% 				\label{fg:ic_wsr_txrx}
		% 				\resizebox{!}{5cm}{
		% 					\input{../assets/simulation/ic_wsr_txrx.tex}
		% 				}
		% 			}
		% 			\caption{
		% 				Average leakage interference and weighted sum-rate versus \gls{ris} and \gls{mimo} interference channel configurations.
		% 				`Alternate' refers to the alternating optimization and `Decouple' refers to the low-complexity design.
		% 				`D' means \gls{d}-\gls{ris} and `BD' refers to fully-connected \gls{bd}-\gls{ris}.
		% 			}
		% 		\end{figure}

		% 		Fig.~\ref{fg:ic_interference_sx} illustrates how \gls{bd}-\gls{ris} helps to reduce the leakage interference.
		% 		In this case, a fully-connected $2^n$-element \gls{bd}-\gls{ris} is almost as good as a $2^{n+2}$-element \gls{d}-\gls{ris} in terms of leakage interference.
		% 		The result also implies that \gls{bd}-\gls{ris} can achieve a higher \gls{dof} than diagonal \gls{ris} in \gls{mimo} interference channel, which generalizes Proposition \ref{pp:dof} and emphasizes the potential of \gls{bd}-\gls{ris} in interference alignment.

		% 		Fig.~\ref{fg:ic_wsr_beamforming} compares the average \gls{wsr} achieved by the optimal and low-complexity beamforming designs, respectively.
		% 		Unlike the point-to-point case, the latter is not as effective as the former.
		% 		The reason is that, for $K$ transmissions of different path loss, interference alignment using only a shared passive beamformer is very challenging especially, when the direct channels are dominant.
		% 		On the other hand, using $K$ precoders in the joint beamforming design can reasonably orthogonalize the channels and the \gls{ris} can simply enhance the signal power.
		% 		A narrower performance gap is expected when $N_\mathrm{S}$ increases or \gls{ris} coverage area shrinks.

		% 		Figs.~\ref{fg:ic_wsr_sx} and \ref{fg:ic_wsr_txrx} show the average \gls{wsr} versus the number of scattering elements and transceiving antennas.
		% 		Again, we observe that the rate gain of \gls{bd}-\gls{ris} over \gls{d}-\gls{ris} increases with $N_\mathrm{S}$, $N_\mathrm{T}$, and $N_\mathrm{R}$.
		% 		The reasons have been discussed in the point-to-point case.

		% 		\begin{figure}[H]
		% 			\centering
		% 			\resizebox{!}{5cm}{
		% 				\input{../assets/simulation/ic_wsr_pair.tex}
		% 			}
		% 			\caption{Impact of channel estimation error and transceiver pairs on the weighted sum-rate of $(2 \times 64 \times 2)^K$ \gls{mimo} interference channel with $P = \qty{20}{dB}$ and $N_\mathrm{E} = 2$.
		% 			}
		% 			\label{fg:ic_wsr_pair}
		% 		\end{figure}

		% 		Fig.~\ref{fg:ic_wsr_pair} shows the average \gls{wsr} versus the backward/forward channel estimation error and the number of transceiver pairs.
		% 		We observe that the proposed joint beamforming design is reasonably robust to channel estimation error and thus viable for practical implementation.
		% 		On the other hand, introducing a \gls{ris} to interference channel systems is helpful to mitigate the rate saturation effect as $K$ increases.
		% 		In the saturated regime ($K \ge 4$), \gls{bd}-\gls{ris} provides a much larger \gls{wsr} than \gls{d}-\gls{ris} thanks to its superior shaping capability in aligning the interference subspaces.
		% 		These results provide valuable insights for practical \gls{ris} design in dense connection scenarios, where proper \gls{bd} configurations can significantly enhance the network capacity.
		% 	\end{subsubsection}
		% \end{subsection}
	}
\end{reviewer}

\bibliographystyle{IEEEtran}
\bibliography{response}
\end{document}
